---
output: html_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup-197844, eval = F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
source('scripts/packages.R')
source('scripts/tables.R')

```

```{r  load-data-197844}
my_site <- 197844

```

# Bighorn Creek - 197844 - Appendix {-}

## Site Location {.unnumbered}

PSCIS crossing `r as.character(my_site)` is located on a tributary to Bighorn Creek on the Cabin FSR. The site is located approximately 11km west of the junction with the Wigwam FSR at a point approximately 30k south of Morrissey. Cabin FSR(forest file ID 5466) is ultimately the responsibility of Ministry of Forests, Lands, Natural Resource Operations and Rural Development - Rocky Mountain Forest District. Although unconfirmed, Canfor may have a road use permit for this section of FSR.

<br>

## Background {.unnumbered}

```{r tab-wshd-197844, eval = F}
fpr::fpr_table_wshd_sum(site_id = my_site) %>% 
  select(-'Elev Min') %>% 
  fpr::fpr_kable(caption_text = paste0('Summary of derived upstream watershed statistics for PSCIS crossing ', my_site, '.'),
           footnote_text = 'Elev P60 = Elevation at which 60% of the watershed area is above',
           scroll = F)

```


PSCIS crossing `r as.character(my_site)` was assessed in 2021 by [@irvine2022ElkRiver] and ranked as a barrier for upstream fish migration. There was 0.8km of steep but viable juvenile rearing habitat surveyed upstream of crossing 197844 in 2021. A detailed write up of habitat details and stream characteristics can be found in the 2021 report memo linked [here](https://www.newgraphenvironment.com/fish_passage_elk_2021_reporting/appendix---197844---tributary-to-bighorn-creek.html). A summary of habitat modelling outputs is presented in Table
\@ref(tab:tab-culvert-bcfp-197844) and a map of the watershed is
provided in map attachment
[`r fpr::fpr_my_bcfishpass(col_pull = dbm_mof_50k_grid)`](`r fpr::fpr_my_mapsheet(wshd = "elkr", archive_date = "2022-03-17")`).
 
`r if(identical(gitbook_on, FALSE)){knitr::asis_output("\\pagebreak")}`

<br>

```{r tab-culvert-bcfp-197844, eval = T}
fpr::fpr_table_bcfp(scroll = gitbook_on) 
```

<br>

## Fish Sampling {.unnumbered}

Electrofishing was conducted with results summarised in Tables
\@ref(tab:tab-fish-site-197844) - \@ref(tab:tab-fish-dens-197844) and Figure
\@ref(fig:plot-fish-box-197844). Habitat details are summarised in Table
\@ref(tab:tab-habitat-summary-197844).  Note that the first site (197844_ds_ef1) was located on the mainstem of Bighorn Creek, while all other sites were located on a tributary to Bighorn Creek.

<br>

`r if(gitbook_on){knitr::asis_output("<br>")} else knitr::asis_output("\\pagebreak")`

```{r tab-habitat-summary-197844, eval=T}
tab_hab_summary %>% 
  filter(Site  == my_site) %>% 
  fpr::fpr_kable(caption_text = paste0('Summary of habitat details for electrofishing sites upstream and downstream of PSCIS crossing ', my_site, '.'),
                 scroll = F) 

```

<br>

```{r tab-fish-site-197844, eval=T}
fpr_table_fish_site()

```

<br>

```{r tab-fish-dens-197844, eval=T}
fpr_table_fish_density()

```

`r if(gitbook_on){knitr::asis_output("<br>")} else knitr::asis_output("\\pagebreak")`

```{r plot-fish-box-197844, fig.cap= my_caption, eval=T}
my_caption <- paste0('Densites of fish (fish/100m2) captured downstream of PSCIS crossing ', my_site, '.')

fpr_plot_fish_box() 

```

