---
output: html_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup-197559, eval = F}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
source('scripts/packages.R')
source('scripts/tables.R')

```

```{r  load-data-197559}
my_site <- 197559

```

# Brule Creek - 197559 - Appendix {-}

## Site Location {.unnumbered}

PSCIS crossing `r as.character(my_site)` is located on
Highway 43 approximately 20km north of the town of
Sparwood. Crossing
`r as.character(my_site)` was located approximately 0.7km upstream from the confluence with the Elk River and is the
responsibility of the Ministry of Transportation and Infrastructure.

<br>

```{r tab-wshd-197559, eval = F}
fpr::fpr_table_wshd_sum(site_id = my_site) %>% 
  select(-'Elev Min') %>% 
  fpr::fpr_kable(caption_text = paste0('Summary of derived upstream watershed statistics for PSCIS crossing ', my_site, '.'),
           footnote_text = 'Elev P60 = Elevation at which 60% of the watershed area is above',
           scroll = F)

```

A summary of habitat modelling outputs is presented in Table
\@ref(tab:tab-culvert-bcfp-197559) and a map of the watershed is
provided in map attachment
[`r fpr::fpr_my_bcfishpass(col_pull = dbm_mof_50k_grid)`](`r fpr::fpr_my_mapsheet(wshd = "elkr", archive_date = "2022-03-17")`).

`r if(identical(gitbook_on, FALSE)){knitr::asis_output("\\pagebreak")}`

<br>

```{r tab-culvert-bcfp-197559, eval = T}
fpr::fpr_table_bcfp(scroll = gitbook_on) 
```


## Fish Sampling {.unnumbered}

Electrofishing was conducted with results summarised in Tables
\@ref(tab:tab-fish-site-197559) - \@ref(tab:tab-fish-dens-197559). Habitat details are summarised in Table
\@ref(tab:tab-habitat-summary-197559). 

`r if(gitbook_on){knitr::asis_output("<br>")} else knitr::asis_output("\\pagebreak")`

```{r tab-habitat-summary-197559, eval=T}
tab_hab_summary %>% 
  filter(Site == my_site) %>% 
  fpr::fpr_kable(caption_text = paste0('Summary of habitat details for electrofishing sites upstream of PSCIS crossing ', my_site, '.'),
                 scroll = F) 

```

<br>

```{r tab-fish-site-197559, eval=T}
fpr_table_fish_site()

```

<br>

```{r tab-fish-dens-197559, eval=T}
fpr_table_fish_density()

```
